The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-20 analysis/paper/paper.qmd

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                        # Managing paths
  "tidyverse",                                   # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm", "topicmodels",  # Text processing and analysis
  "tidygeocoder",                                # Working with spatial data
  "igraph", "ggraph"                             # Network analysis and visualization
)

@@

Similar to topic clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                        # Managing paths
  "tidyverse", "reshape2",                       # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm", "topicmodels",  # Text processing and analysis
  "tidygeocoder",                                # Working with spatial data
  "igraph", "ggraph"                             # Network analysis and visualization
)

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

```{r}
# The topicmodels package requires a document-term matrix as input
emu_theses_dtm <- emu_theses_words |> 
  count(title, word, sort = TRUE) |> 
  cast_dtm(title, word, n)

emu_theses_dtm

# We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling
# In LDA, each document is a mixture of topics and each topic is a mixture of words
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

# Tidy model with beta statistic
emu_theses_topics <- tidy(emu_theses_lda, matrix = "beta")
emu_theses_topics

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(20, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)

emu_theses_top_terms |> 
  mutate(term = reorder(term, beta)) |> 
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

# 
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))

beta_spread

beta_spread %>%
  group_by(direction = log_ratio > 0) %>%
  slice_max(abs(log_ratio), n = 20) %>% 
  ungroup() %>%
  mutate(term = reorder(term, log_ratio)) %>%
  ggplot(aes(log_ratio, term)) +
  geom_col() +
  labs(x = "Log2 ratio of beta in topic 2 / topic 1", y = NULL)

emu_theses_documents <- tidy(emu_theses_lda, matrix = "gamma")
emu_theses_documents

emu_theses_documents |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip()

emu_theses_documents |> 
  inner_join(emu_theses |> select(title, graduation_year), by = c("document" = "title")) |> 
  ggplot(aes(x = reorder(str_sub(document, 1, 50), gamma), y = gamma, fill = topic)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  facet_wrap(~ graduation_year, ncol = 1, scales = "free", drop = TRUE)

emu_theses_documents |> 
  inner_join(emu_theses |> select(title, graduation_year), by = c("document" = "title")) |> 
  ggplot(aes(x = factor(graduation_year), y = topic, fill = factor(topic))) +
  geom_col()
```
